---
title: "rockthemes"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->


<!-- badges: end -->


## What?

This is a collection of colour palettes based on classic rock album covers.

Although 'rock' may be a stretch in some cases, the albums were chosen for their
appealing covers

## Why?

Because [this repo of Metallica inspired palettes](https://github.com/johnmackintosh/metallicaRt) has been received quite well on various social media platforms




## Credit

[Thanks to Ryo for the tvthemes package](https://github.com/Ryo-N7/tvthemes) which helped me get this off the ground quickly


## I want this

Of course you do. 
This will not go to CRAN, so please install using the remotes package.

```{r}
#library(remotes)
#remotes::install_github("johnmackintosh/rockthemes")
library(rockthemes)
```

## Data Viz Friendly

These mini palettes are lush


```{r}
rock_palette("californication")

```


```{r}
rock_palette("coltrane")

```


```{r}
rock_palette("electric")
```


```{r}
rock_palette("faithnomore")

```



```{r}
rock_palette("gogo")
m <- outer(1:20,1:20,function(x,y) sin(sqrt(x*y)/3))
cols <- rock_palette("gogo")
Lab.palette <- colorRampPalette(cols,space = "Lab")
filled.contour(m, col = Lab.palette(20))
```



```{r}
rock_palette("gunsnroses")
```



```{r}
rock_palette("harvey")
```


```{r}
rock_palette("heap")
```


```{r}
rock_palette("herb")
```


```{r}
rock_palette("husker")
```



```{r}
rock_palette("maiden")
```


```{r}
rock_palette("metallica")
```



```{r}
rock_palette("miles")
```


```{r}
rock_palette("nevermind")
```


```{r}
rock_palette("oasis")
```


```{r}
rock_palette("swift")
```


```{r}
rock_palette("tencc")
```


